Real-time resolution of short-read assembly graph using ONT long reads

### 2020-03-06 plos_latex_template.tex
data availability

\begin{table}[!ht]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{Comparison of assemblies produced in batch-mode using \npgraph{} and other hybrid assembly methods on representative \unicycler{}`s synthetic data downloaded from \url{https://cloudstor.aarnet.edu.au/plus/index.php/s/dzRCaxLjpGpfKYW}} 
\label{table:npgraph_compare}
\begin{tabular}{llcrrrrr@{\hspace{2pt}}c@{\hspace{2pt}}r}
 \hline
    &       & \cthead{1}{Assembly} &     & 
    \cthead{1}{N50}  & \cthead{1}{Mis-} &  \cthead{1}{Error}  &
    \cthead{3}{Run times} \\
    & \cthead{1}{Method} & \cthead{1}{size (Mbp)} & \cthead{1}{\#Contigs} &
    \cthead{1}{(Kbp)} & \cthead{1}{assemblies} & \cthead{1}{(per 100 Kbp)} &  
    \cthead{3}{(CPU hrs)} \\
\thickhline

@@

% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
\paragraph*{S1 Fig.}
\label{S1_Fig} Dotplot generated by MUMmer for assembly results of \unicycler{} versus \npgraph{}. Structural agreements between two methods were found in (a)~\emph{C.freundii} and (b)~\emph{K.oxytoca} assembly contigs. On the other hand, for (c)~\emph{E.cloacae} sample, there was a disagreement detected between 2 largest contigs given by two assembly algorithms.

\begin{figure}[!ht]
 \includegraphics[width=\textwidth]{images/FigS1.eps}
 \caption{Dotplot generated by MUMmer for assembly results of \unicycler{} versus \npgraph{}}
\end{figure}

\paragraph*{S2 Fig.}
\label{S2_Fig} Alignments of an \emph{Enterobacter~cloacae} reference genome to assembly sequences generated by  (a)~\unicycler{} and (b)~\npgraph{}. The former suggests a structural variant, the latter is virtually an 1-to-1 mapping.

\begin{figure}[!ht]
 \includegraphics[width=\textwidth]{images/FigS2.eps}
 \caption{Alignments of an \emph{Enterobacter~cloacae} reference genome to assembly sequences generated by  (a)~\unicycler{} and (b)~\npgraph{}}
\end{figure}

\paragraph*{S1 Table.}
\label{S1_Table}
Benchmarking \npgraph{} against \npscarf{} versions, $\mathtt{hybridSPAdes}$ and \unicycler{} hybrid assembler with the synthetic data set.

@@

\begin{longtable}[!hpt]{llcrrrrr}
%\caption{Benchmarking \npgraph{} against \npscarf{} versions, $\mathtt{hybridSPAdes}$ and \unicycler{} hybrid assembler with the synthetic data set.}
\toprule
    &       & Assembly &  & N50  & Mis- &  Mismatch & Indel \\
    & Method & size (bp) & \#Contigs  & (bp) & assemblies & (per $100$Kbp) & (per $100$Kbp) \\
    \hline  
\endfirsthead
\multicolumn{8}{c}%
{\tablename\ \thetable\ -- \textit{Continued from previous page}} \\
\hline
    &       & Assembly &  & N50  & Mis- &  Mismatch & Indel \\
    & Method & size (bp) & \#Contigs  & (bp) & assemblies & (per $100$Kbp) & (per $100$Kbp) \\
\hline
\endhead
\hline \multicolumn{8}{r}{\textit{Continued on next page}} \\
\endfoot
\hline
\endlastfoot

@@

\section*{Acknowledgments}
Cras egestas velit mauris, eu mollis turpis pellentesque sit amet. Interdum et malesuada fames ac ante ipsum primis in faucibus. Nam id pretium nisi. Sed ac quam id nisi malesuada congue. Sed interdum aliquet augue, at pellentesque quam rhoncus vitae.

>>>>

\begin{table}[!ht]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{Comparison of assemblies produced in batch-mode using \npgraph{} and other hybrid assembly methods on synthetic data.} 
\label{table:npgraph_compare}
\begin{tabular}{llcrrrrr@{\hspace{2pt}}c@{\hspace{2pt}}r}
 \hline
    &       & \cthead{1}{Assembly} &     & 
    \cthead{1}{N50}  & \cthead{1}{Mis-} &  \cthead{1}{Error}  &
    \cthead{3}{Run times} \\
    & \cthead{1}{Method} & \cthead{1}{size (Mbp)} & \cthead{1}{\#Contigs} &
    \cthead{1}{(Kbp)} & \cthead{1}{assemblies} & \cthead{1}{(per 100 Kbp)} &  
    \cthead{3}{(CPU hrs)} \\
\thickhline

@@

% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
\paragraph*{S1 Fig.}
\label{S1_Fig} Dotplot generated by MUMmer for assembly results of \unicycler{} versus \npgraph{}.

\begin{figure}[!ht]
 \includegraphics[width=\textwidth]{images/FigS1.eps}
 \caption{Dotplot generated by MUMmer for assembly results of \unicycler{} versus \npgraph{}. Structural agreements between two methods were found in (a)~\emph{C.freundii} and (b)~\emph{K.oxytoca} assembly contigs. On the other hand, for (c)~\emph{E.cloacae} sample, there was a disagreement detected between 2 largest contigs given by two assembly algorithms.}
\end{figure}

\paragraph*{S2 Fig.}
\label{S2_Fig} Alignments of an \emph{Enterobacter~cloacae} reference genome to assembly sequences generated by  (a)~\unicycler{} and (b)~\npgraph{}

\begin{figure}[!ht]
 \includegraphics[width=\textwidth]{images/FigS2.eps}
 \caption{Alignments of an \emph{Enterobacter~cloacae} reference genome to assembly sequences generated by  (a)~\unicycler{} and (b)~\npgraph{}. The former suggests a structural variant, the latter is virtually an 1-to-1 mapping.}
\end{figure}

\clearpage
\paragraph*{S1 Table.}
\label{S1_Table}
Benchmarking \npgraph{} against \npscarf{} versions, $\mathtt{hybridSPAdes}$ and \unicycler{} hybrid assembler with the synthetic data set.

@@

\begin{longtable}[!hpt]{llcrrrrr}
%\caption{Benchmarking \npgraph{} against \npscarf{} versions, $\mathtt{hybridSPAdes}$ and \unicycler{} hybrid assembler with the synthetic data set.}
%\label{supp_tab:synthetic_benchmark}\\
\toprule
    &       & Assembly &  & N50  & Mis- &  Mismatch & Indel \\
    & Method & size (bp) & \#Contigs  & (bp) & assemblies & (per $100$Kbp) & (per $100$Kbp) \\
    \hline  
\endfirsthead
\multicolumn{8}{c}%
{\tablename\ \thetable\ -- \textit{Continued from previous page}} \\
\hline
    &       & Assembly &  & N50  & Mis- &  Mismatch & Indel \\
    & Method & size (bp) & \#Contigs  & (bp) & assemblies & (per $100$Kbp) & (per $100$Kbp) \\
\hline
\endhead
\hline \multicolumn{8}{r}{\textit{Continued on next page}} \\
\endfoot
\hline
\endlastfoot

@@

\section*{Data availability}
All data used for benchmarking were from public sources. The synthetic data was downloaded from \url{https://cloudstor.aarnet.edu.au/plus/index.php/s/dzRCaxLjpGpfKYW}. The real bacterial sequencing data was from NCBI under project accession number PRJNA353060.

\section*{Acknowledgments}
